Blocking-resistant communication\\through domain fronting

### 2014-11-23 docs/meek.tex
Trimming, revisions.

\begin{figure}
\includegraphics[width=\linewidth]{clients-psiphon3}
\caption{
Daily unique users of \meek\ with
[blinded circumvention tool]
% ANON
% Psiphon
(note vertical axis).
The decrease at the end of June
was caused by an unblocking event that made \meek\ unnecessary for some users.
}
\label{fig:clients-psiphon3}
\end{figure}

Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
since close to the beginning of development.
A measurement of 5, for example, means that there were on average five
simultaneous users of the system at any time during the day.
The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
which aggregates statistics reported by Tor relays.
The number of users is estimated by counting the number
of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.

[Blinded circumvention tool]
% ANON
% Psiphon
began their independent deployment of \meek\ in June~2014.
Figure~\ref{fig:clients-psiphon3} shows the number
of unique daily users of \meek%
,
% ANON
% with Psiphon,
estimated through clients' self-reporting of their most recent connection date.
The developers tell us that the drop that occurs
in the middle of June was not caused by a blocking event,
but rather an unblocking event that made \meek\ unnecessary for some users.
Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
are not directly comparable because they count slightly different things,
it is clear that meek-with-%
[blinded circumvention tool],
% ANON
% Psiphon,
with its thousands of daily users,
is much more widely used than meek-with-Tor, which has not yet seen a formal release.

@@

Figure~\ref{fig:ciphersuites} illustrates the need for camouflage at the TLS layer.
Even though the TLS application data is effectively hidden by encryption,
the plaintext parts of TLS reveal information about the implementation.
The TLS must not be easily identified as belonging to a circumvention tool.

@@

\caption{
Selected differences in ClientHello messages in three different TLS implementations.
}
\label{fig:ciphersuites}
\end{figure*}

>>>>

% \begin{figure}
% \includegraphics[width=\linewidth]{clients-psiphon3}
% \caption{
% Daily unique users of \meek\ with
% [blinded circumvention tool]
% % ANON
% % Psiphon
% (note vertical axis).
% The decrease at the end of June
% was caused by an unblocking event that made \meek\ unnecessary for some users.
% }
% \label{fig:clients-psiphon3}
% \end{figure}

Figure~\ref{fig:clients-tor} shows the average number of concurrent users of \meek\ with Tor
since close to the beginning of development.
A measurement of 500, for example, means that there were on average 500
users of the system at any given time during the day.
The measurements come from the Tor Metrics Portal~\cite{metrics-meek},
which aggregates statistics reported by Tor relays.
The number of users is estimated by counting the number
of Tor directory requests made by clients~\cite{counting-daily-bridge-users}.
% The drop to zero on May~8 coincides with the reinstallation of the Tor bridge used by \meek.

% [Blinded circumvention tool]
% % ANON
% % Psiphon
% began their independent deployment of \meek\ in June~2014.
% Figure~\ref{fig:clients-psiphon3} shows the number
% of unique daily users of \meek%
% ,
% % ANON
% % with Psiphon,
% estimated through clients' self-reporting of their most recent connection date.
% The developers tell us that the drop that occurs
% in the middle of June was not caused by a blocking event,
% but rather an unblocking event that made \meek\ unnecessary for some users.
% Although Figures~\ref{fig:clients-tor} and~\ref{fig:clients-psiphon3}
% are not directly comparable because they count slightly different things,
% it is clear that meek-with-%
% [blinded circumvention tool],
% % ANON
% % Psiphon,
% with its thousands of daily users,
% is much more widely used than meek-with-Tor, which has not yet seen a formal release.

@@

@@

\caption{
Selected differences in ClientHello messages in three different TLS implementations.
This figure illustrates the need for camouflage at the TLS layer.
Even though the TLS application data is effectively hidden by encryption,
the plaintext parts of TLS reveal information about the implementation.
The TLS must not be easily identified as belonging to a circumvention tool.
}
\label{fig:ciphersuites}
\end{figure*}
